Title of the Master Thesis

### 2015-10-12 Master Thesis/synopsis.tex
Fix multiple identical labels
Clarify definition of admissible pair
Fix

\begin{lemma}\label{3.2}
$\sigma$ induces a bijection $\sigma:\operatorname{Spv}_\text{d}^{(1)}(K)\to\operatorname{Spv}_\text{d}^{(1)}(K')$. If $E=K_v\subset\overline{K}$ is a henselization of $K$ with respect to $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$ then $E'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. Furthermore, if $E^{\text{t}}$ and $E'^{\text{t}}$ denotes the inertial fields of $E$ and $E'$ respectively, then $\sigma$ induces an isomorphism:
\[ G_{k(v)}\cong\operatorname{Gal}(E^\text{t}/E)\to\operatorname{Gal}(E'^{\text{t}}/E')\cong G_{k(v')} \]
which is induced by a unique isomorphism $\varphi_v^\text{s}:k(v')^\text{s}\to k(v)^\text{s}$. In particular $\varphi_v=\varphi_v^\text{s}|_{k(v')}:k(v')\to k(v)$ is an isomorphism.
\end{lemma}

@@

\paragraph{}\label{4.3} Let $n\in\mathbb{N}$. For all intermediate fields $L$ of $\overline{K}/K$, $\sigma$ induces an isomorphism:
\[ \varphi_n:L'^\times/n \cong\mathrm{H}^1(L', \mu_n) \to \mathrm{H}^1(L,\mu_n) \cong L^\times/n \]
Obviously, for intermediate fields $L\subset M$ of $\overline{K}/K$ the following diagram commutes:
\[ \begin{tikzcd}
L'^\times/n \ar[r, "\varphi_n"]\dar & L^\times/n \dar\\
M'^\times/n \ar[r, "\varphi_n"'] & M^\times/n
\end{tikzcd} \]
Let $P\in X_0$ and $v_P:K\to\mathbb{Z}\cup\{\infty\}$ be the corresponding discrete normalized valuation and let $U_P$ be the group of units of the valuation ring $\mathcal{O}_P$. We denote the residue map $U_P\to k(P)^\times,\ x\mapsto x\mod P$ by $r_P$. For $n\in\mathbb{N}$ the following sequence is exact:
\[ 0\to U_P/n\to K^\times/n\to\mathbb{Z}/n\mathbb{Z}\to 0 \]

@@

\begin{definition}\label{4.4}
For a finite subset $S\subset X_0$ set:
\[ K^S=\{x\in K^\times \mid v_P(x)=0\text{ for all }P\in X_0\setminus S \} \]
$K'^{S'}$ is defined similarly. For finite subsets $S$ of $X_0$, the corresponding subsets of $X_0'$ will be denoted by $S'$, i.e. $S'=\sigma(S)$.
\end{definition}

@@

@@

\begin{step}
There exists a unique group isomorphism $\varphi:K'^\times\to K^\times$ such that for any $P\in X_0$ we have $\varphi(U_{P'})=U_P$ where $P'=\sigma(P)$ and the following diagram commutes:
\[ \begin{tikzcd}
U_{P'} \ar[r, "\varphi"]\ar[d, "r_{P'}"'] & U_P \ar[d, "r_P"]\\
k(P') \ar[r, "\varphi_P"'] & k(P)
\end{tikzcd} \]
\end{step}

>>>>

\begin{lemma}\label{3.2}
$\sigma$ induces a bijection $\sigma:\operatorname{Spv}_\text{d}^{(1)}(K) \to\operatorname{Spv}_\text{d}^{(1)}(K')$. If $E=K_v\subset\overline{K}$ is a henselization of $K$ with respect to $v\in\operatorname{Spv}_\text{d}^{(1)}(K)$, then $E'$ is a henselization of $K'$ with respect to $v'=\sigma(v)$. Furthermore, if $E^{\text{t}}$ and $E'^{\text{t}}$ denote the inertial fields of $E$ and $E'$ respectively, then $\sigma$ induces an isomorphism:
\[ G_{k(v)}\cong\operatorname{Gal}(E^\text{t}/E) \to\operatorname{Gal}(E'^{\text{t}}/E')\cong G_{k(v')} \]
which is induced by a unique isomorphism $\varphi_v^\text{s}:k(v')^\text{s}\to k(v)^\text{s}$. In particular $\varphi_v=\varphi_v^\text{s}|_{k(v')}:k(v')\to k(v)$ is an isomorphism.
\end{lemma}

@@

\paragraph{} Let $n\in\mathbb{N}$. For all intermediate fields $L$ of $\overline{K}/K$, $\sigma$ induces an isomorphism:
\[ \varphi_n:L'^\times/n \cong\mathrm{H}^1(L', \mu_n) \to \mathrm{H}^1(L,\mu_n) \cong L^\times/n \]
Obviously, for intermediate fields $L\subset M$ of $\overline{K}/K$ the following diagram commutes:
\[ \begin{tikzcd}
L'^\times/n \ar[r, "\varphi_n"]\dar & L^\times/n \dar\\
M'^\times/n \ar[r, "\varphi_n"'] & M^\times/n
\end{tikzcd} \]
Let $P\in X_0$ and $v_P:K\to\mathbb{Z}\cup\{\infty\}$ be the corresponding discrete normalized valuation and let $U_P$ be the group of units of the valuation ring $\mathcal{O}_P$. We denote the natural projection $U_P\to k(P)^\times,\ x\mapsto x\mod P$ by $r_P$. For $n\in\mathbb{N}$ the following sequence is exact:
\[ 0\to U_P/n\to K^\times/n\to\mathbb{Z}/n\mathbb{Z}\to 0 \]

@@

\begin{definition}\label{4.4}
For a finite subset $S\subset X_0$ set:
\[ K^S=\{x\in K^\times \mid v_P(x)=0\text{ for all }P\in X_0\setminus S \} \]
$K'^{S'}$ is defined similarly. For finite subsets $S$ of $X_0$, the corresponding subsets of $X_0'$ will be denoted by $S'$, i.e. $S'=\{\sigma P\mid P\in S \} $.
\end{definition}

@@

\begin{definition}
For each admissible $S\subset X_0$ we can find a finite subset $T\subset X_0\setminus S$ such that both $r_{S,T}$ and $r_{S',T'}$ are injective. Such a $T$ will be called $S$-\textit{admissible} and $(S,T)$ is called \textit{admissible pair}.
\end{definition}

@@

\begin{step}
There exists a unique group isomorphism $\varphi:K'^\times\to K^\times$ such that for any $P\in X_0$ we have $\varphi(U_{P'})=U_P$ where $P'=\sigma(P)$ and the following diagram commutes:
\[ \begin{tikzcd}
U_{P'} \ar[r, "\varphi"]\ar[d, "r_{P'}"'] & U_P \ar[d, "r_P"]\\
k(P')^\times \ar[r, "\varphi_P"'] & k(P)^\times
\end{tikzcd} \]
\end{step}
